---
title: "ALBEDO Ray Tracing: Acceleration Structure Comparative Benchmark Report"
author: "ALBEDO Benchmark & Analysis Suite"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    theme: readable
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(readr)
library(knitr)

source("load_results.R")
source("plots.R")
source("significance_tests.R")
source("sah_correlation.R")

latest_csv <- find_latest_benchmark_csv("../../benchmark_results", type = "reps")
df <- load_benchmark_results(latest_csv)
```

# Executive Summary

This report delivers a rigorous empirical and statistical evaluation of the acceleration structures implemented within **ALBEDO**:

- **Binned-SAH (Serial & Parallel)**: Baseline surface area heuristic binary BVH.
- **Wide BVH4 (4-wide SIMD)**: 4-ary wide BVH evaluated via 128-bit vector SSE instructions.
- **Wide BVH8 (8-wide AVX2)**: 8-ary wide BVH evaluated via native 256-bit AVX2 instructions.
- **TLAS (Two-Level AS)**: Top-level acceleration structure for instanced geometries.

---

# Traversal Throughput Evaluation

```{r throughput_plot, fig.width=10, fig.height=6}
plot_throughput_comparison(df)
```

---

# Construction Performance (Parallel Scaling)

```{r build_plot, fig.width=9, fig.height=5}
plot_build_time_comparison(df)
```

---

# Topology & Compaction

```{r node_plot, fig.width=9, fig.height=5}
plot_node_count_comparison(df)
```

---

# Paired Significance Testing (Wilcoxon Signed-Rank)

Statistical hypothesis testing conducted against baseline with Benjamini-Hochberg False Discovery Rate ($\alpha = 0.05$):

```{r significance_table}
sig_df <- run_significance_tests(df, baseline = "Binned-SAH (Serial)", output_dir = "results")
if (nrow(sig_df) > 0) {
  kable(sig_df %>% select(scene, ray_set, candidate, metric, baseline_median, candidate_median, speedup, p_adj_bh, is_significant),
        digits = 3,
        caption = "Paired Wilcoxon Signed-Rank Significance Tests vs Baseline")
}
```

---

# Statistical Methodology Notes

1. **Repetitions & Pairing**: Each scenario is evaluated over 5 deterministic repetitions with identical random seeds.
2. **Error Bars**: Represent empirical Interquartile Range ($25^{\text{th}} - 75^{\text{th}}$ percentiles) avoiding unverified normality assumptions.
3. **Multiple Testing**: Benjamini-Hochberg procedure controls FDR across the family of hypotheses.
